---
title: "Cocao Analysis"
output: 
  html_document:
    number_sections: false
    toc: true
    toc_depth: 6
    highlight: tango
    theme: yeti
    code_folding: show
    df_print: kable
---

## Load libraries

```{r import csv, include=FALSE}
library(tidyverse)
library(ggplot2)
library(readr)
library(stringr)
library(lubridate)
library(dplyr)
library(rworldmap)
```

## Import CSV

```{r  message = FALSE, warning = FALSE, error = FALSE}
full_data <- read_csv('~/Downloads/flavors_of_cacao.csv')

```

## View dataset columns

You can see the column name include space and line break. If we don't clean that it might cause error in ggplot.

```{r pressure, echo=FALSE}
names(full_data)
```

### Clean columns name format

```{r clean_column_names}
# Remove and replace spaces and line breaks
names(full_data) <- tolower(gsub(pattern = '[[:space:]+]', '_', names(full_data)))

# View the new column names 
names(full_data)
```

### Explain the columns in Chinese

1.  "company_maker": 制造巧克力的公司或品牌的名称。
2.  "specific_bean_origin_or_bar_name": 指定可可豆的原产地或巧克力棒的名称。这个列可能包含有关可可豆种类或巧克力产品的其他特定信息。
3.  "ref": 参考编号，可能是与巧克力产品或数据相关的参考编号。
4.  "review_date": 评论日期，指示对巧克力进行评价的日期。
5.  "cocoa_percent": 可可含量，表示巧克力中可可固体的百分比。
6.  "company_location": 制造公司的所在地或总部所在地。
7.  "rating": 对巧克力产品的评级或评分。
8.  "bean_type": 可可豆的类型或品种。
9.  "broad_bean_origin":可可豆的产地或原产地，指示制作巧克力所用可可豆的来源。

## Explore the data

Just find anything I interested

### Data collection date

```{r echo=FALSE}
ggplot(data=full_data) + geom_bar(mapping = aes(x=review_date)) 
```

## Cocoa percentage

```{r}

# 将百分比字符串转换为数值
full_data$cocoa_percent_numeric <- as.numeric(sub("%", "", full_data$cocoa_percent)) / 100

# 设置刻度间距为每隔10%显示一个标签
ggplot(data = full_data) + 
  geom_jitter(mapping = aes(x = review_date, y = cocoa_percent_numeric)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = scales::percent)



```

## broad_bean_origin 统计

"specific_bean_origin_or_bar_name" 是具体地点，broad_bean_origin 对于的地点相对广泛，更利于统计,但是数据仍然需要进一步清洗

```{r}
# 假设您的数据框名为df，列名为specific_bean_origin_or_bar_name
df_counts <- full_data %>%
  group_by(broad_bean_origin) %>%
  summarise(count = n())

# 查看计数结果
print(df_counts)
```

## ref 的含义

由于查询不到ref 的具体含义，先统计查看原因

```{r}
# 假设您的数据框名为df，列名为specific_bean_origin_or_bar_name
ref_counts <- full_data %>%
  group_by(`company _(maker-if_known)`) %>%
  summarise(count = n())

# 查看计数结果
print(ref_counts)
```
没有什么用处。

## Try rworldmap

learning YANGYA's code, It's not teach in coursera's course.

```{r}
omap <- group_by(full_data,broad_bean_origin)
omap1 <- summarise(omap,broad_bean_origin)
map2 <- joinCountryData2Map(omap1,joinCode="NAME",nameJoinColumn = "broad_bean_origin")
mapCountryData(map2, mapTitle = "Cocao Origin Distribution", colourPalette = "negpos9")
```

## Company location

This value means where the chocolate manufacture company base at.

```{r}
cmap <- group_by(full_data,company_location)
cmap1 <- summarise(cmap,count=n())
map3 <- joinCountryData2Map(cmap1,joinCode="NAME",nameJoinColumn = "company_location")
mapCountryData(map3,nameColumnToPlot = "count", mapTitle = "Chocolate Factory Distribution", colourPalette = "negpos8")
```

51 codes from your data successfully matched countries in the map 9 codes from your data failed to match with a country code in the map 192 codes from the map weren't represented in your data about 260 failed data



